Summary

### 2016-02-05 inst/examples/summary.Rmd
ok

```{r publication_time, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
hist(df$publication_year, main = "Document frequencies over time")
```

>>>>

```{r publication_time, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
#hist(df$publication_year, main = "Document frequencies over time")
dfs <- df %>% group_by(publication_year) %>% tally()
ggplot(dfs, aes(x = publication_year, y = n)) + geom_point() + ggtitle("Document frequencies over time") + ylab("Title count") + xlab("Publication year")
```
